\subsubsection{Client requirements}

A user may access the create profile functionality of the application which sets 
up a user-profile for the system. The user can input common user data into the 
input fields available to them on the registration form. These fields 
should include, but not be limited to: username, password and e-mail. 
There should also be fields in the registration form that are more geared
towards the social networking aspect of the program - such as biography, 
country and date of birth. 
\vspace{10pt}
A user must also be able to edit their profile at any given time. A user will 
be able to change whatever information is tied to their profile - 
so long as it is not their username. 

A user must be able to manage and play music from their 
library. The music library should be the most important aspect of the music 
management system, because it is here the user will actually be able to use 
the main functionality of the application - to play music and establish their 
online library. It should also be possible for a user to create a playlist of 
songs and manage it. Playlists should be 
sortable with the traditional orderings (e.g. album, artist and alphabetical 
title sort). The user should also be able to manually sort songs in their
playlists - for example if the user wishes their playlist to start out playing
the quiet songs in their playlist, and end with louder songs, or something else, 
then those sortings should be available.

The application should also support a social aspect which gives a user access to
a community where they may discuss music as well as manage their friend list.
As part of the functionality, Moving Whales should allow users to join up in
sessions and listen to the same song simultaneously with other users and create 
playlists that they can listen to together. A session should have a person that
is the DJ of the music session. A DJ is the administrator of the session and has 
the rights to manipulate the playlist or kicking and inviting people from a 
session. A session should also have a vote system that allows users to 
democratically choose to skip to next song, hop back to the previous song, 
restart the song currently playing or even changing the DJ and other such 
functionality that might be relevant.