\subsection{What is Scrum?}

Scrum is an iterative development method\cite{scrumguide11}.
Ken Schwaber and Jeff Sutherland developed Scrum as a framework for developing 
and sustaining complex products\cite{scrumguide11}. Scrum has been defined by 
Ken Schwaber and Jeff Sutherland, as follows:

\textbf{Scrum (n):} \begin{quotation}
A framework within people can address complex adaptive 
problems, while productively and creatively delivering products of the highest 
possible value\cite{scrumguide11}.
\end{quotation}

With this in mind, there are several key features that defines Scrum.

\begin{itemize}
	\item Lightweight
	\item Simple to understand
	\item Extremely difficult to master\cite{scrumguide11}
\end{itemize}

The Scrum framework consists of 4 key ingredients\cite{scrumguide11}. First and
foremost - the Scrum Team: the Scrum Team is basically anyone who works on the project. Each member in the Team has a 
role - they will be discussed later in this section.
The second ingredient is the events. The events in Scrum are typically meetings. The 
details of the events will be discussed later. The third ingredient is artifacts. Artifacts 
are things that add transparency to the project. For example, the Product Backlog, the 
Sprint Backlog or the burndown chart\cite{scrumguide11}. The fourth ingredient is the rules 
of Scrum. These rules are imperative for the succes of Scrum as they are the glue that binds 
the framework together. Rules are generally the codex that must be adhered to. For example, 
how long a sprint is time boxed, how long the daily Scrum is time boxed and so on. The rules 
govern the practices of Scrum\cite{scrumguide11}.



\input{analysis/scrumtheory}