\section{The Heuristic method}
When we speak of the Heuristic method then we talk about using a number of different methods fore evaluation of a HCI(Human Computer Interaction) design. When one wants to make an evaluation of design, one can have a list of heuristics(also called design principles)to begin with. Here are some examples on some design principles:
\begin{enumerate}
\item Visibility
\item Consistency
\item Navigation
\item Control
\item Constraints
\item Style
\item Conviviality
\end{enumerate}
and a lot more.

\bf{Visibility:} is about making things visible so that people can see what options they have and what the system is currently doing. An important part of the visibility is the psychological principle that states, it is easier to recognize things than to have to recall them. Visibility is not always about making things visible for the eye it is also about making things visible through the use of sound and touch.\\
\bf{Consistency:} makes the usability more friendly and easier to learn a new system. It is important to stay consistent so that users do not get more confused then necessary. There are two types of consistency. There is conceptual consistency and than there is physical consistency. Conceptual consistency is about ensuring the mappings are consistent. Physical consistency is about ensuring consistent behaviours and consistent use of colours, names, layouts and so on.\\
\bf{Navigation:} is about providing functions to the user such the he/she can move around in the system: maps, directional signs and information signs.\\ 
\bf{Control:} it should be obvious who is in control, the user or the system. To enhance the controls there should be clear, logical mapping controls and the effect that they have.\\
\bf{Constraints:} should always be provided in any system such that the user does not do any inappropriate operations. People should be prevented from making serious errors.\\ 
\bf{Style:} Designs should be stylish and attractive. It should keep up with the time and be in vague.\\ 
\bf{Conviviality:} polite, friendly and generally pleasant software is more catchy than unpleasant software. When making interactive systems it is mandatory to take this in mind fore else if not considered one may end up with some product that loses audience.

When those principles and more have been evaluated, one can get a pretty good picture of the whole system before launching it.%det her skal nok lige omformuleres lidt eller slettes
To move the evaluation of the design of a system further we get to a point where people/future users have to be brought into the evaluation. They have to help one understand their needs, desires and how they are using the system such that developers can redesign some features if needed. %læs lige det her igennem endnu en gang og se om der er noget der nok lige skal skrives om.

When all this is said it does not mean that this is the only approach for evaluating design. There are lots of other methods and principles for evaluation of system designs. 

%%kilde: DIEB bogen%%
