\begin{longtable}{ | p{4.7cm} | p{5.1cm} |}
  \hline
  Steps & Notes \\ \hline
  1. Using the scenarios prepared earlier, write a draft list of tasks & Tasks must be realistic, do-able with the software and explore the system thoroughly \\ \hline
	2. Try out the tasks and estimate how long they will take a participant to complete & Allow 50 percent longer than the total task time for each test session \\ \hline
	3. Prepare a task sheet for the participants & Be specific and explain the task so that everyone can understand. \\ \hline
	4. Get ready for the test session & Have the prototype ready in a suitable environment with a list of prompt questions, notebook and pens ready. A video or audio recorder would be very useful here. \\ \hline
	5. Tell the participants that it is the system that is under test, not them; explain and introduce the tasks. & Participants should work individually - you will not be able to monitor more than one participant at once. Start recording if the equipment is available. \\ \hline
	6. Participants start the tasks. Have them give you running commentary on what they are doing, why they are doing it and difficulties or uncertainties they encounter. & Take notes of where participants find problems or do something unexpected, and their comments. Do this even if you are recording the session. You may need to help if participants are stuck or have them move to the next task. \\ \hline
	7. Encourage participants to keep talking. & Some useful prompt questions are provided below. \\ \hline
	8. When the participants have finished, interview them briefly about the usability of the prototype and the session itself. Thank them. & Some useful questions are provided below. If you have a large number of participants, a simple questionnaire may be helpful. \\ \hline
	9. Write up your notes as soon as possible and incorporate into a usability report. & \\ \hline
\end{longtable}